---
title: "DOSPERT Norming Analyses"
author: "lilly kofler"
date: '`r Sys.Date()`'
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: paper
    toc: yes
    toc_depth: 4
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '4'
subtitle: draft 1
---
```{r, echo=T, warning=FALSE, message=FALSE}
#install dospert package 
#devtools::install_github("schafik/dospert")

#load libraries
library(base)
library(stats)
library(plyr)
library(dplyr)
library(stringr)
library(ggplot2)
library(decider)
library(dospert)
library(Hmisc)
library(psych)
library(texreg)



#setwd to project 
setwd("~/Dropbox/Dospert_Norming_Firstwave_Analyses")

#read in cleaned norming data 
dospert_norm_data <- readRDS("Dospert_Norm_Data.RDS")

```

```{r, echo=T, warning=FALSE, message=FALSE}
#new dospert function using regular expressions

dd_score <- function(df, var, file_type = "csv"){


  uniqR_csv <- function(df, var) {
    df <- df %>% rename_(unique_ID = as.symbol(var))
    df <- df[-1, ]
  }

  # for .xml, use the identified variable as unique_id
  uniqR_xml <- function(df, var){
    df <- df %>% rename_(unique_ID = as.symbol(var))
  }

  wideformat <- function(df, var, file_type){
    if(file_type == "csv"){
      df <- uniqR_csv(df, var)
    } else if (file_type == "xml") {
      df <- uniqR_xml(df, var)
    }

    return(df)
  }

  d_clean <- function(df, var, file_type){

    # for .csv, use the identified variable as unique_ID and remove the first row (variable name,)
    full.panel <- function(df){

      fac_friendly <- function(x) {
        x <- as.numeric(as.character(x))
      }
      selectcol <- function(df){

        pat = "[a-z]{3}[A-Z]{2}_[0-9]{1}|unique_ID"
        df <- df[ , grepl( pat, colnames(df))]

        df[ , !(colnames(df) == "unique_ID")] <- df %>%
          select(-unique_ID) %>% mutate_each(funs(fac_friendly))

        ## making sure correct type of conversion
        return(df)
      }

      # panelform function is used in [full.panel] function
      # changes input df into longform and identifies the question
      # domain, number and type (e.g. fin 6 RT, 6th question in
      # finance domain, of Risk Taking)
      panelform <- function(df) {
        wide <- reshape2::melt(df, id.vars = "unique_ID")
        wide$domain <- substr(wide$variable, 1, 3)
        wide$Qnumber <- substr(wide$variable, 7, 7)
        wide$type <- substr(wide$variable, 4, 5)

        wide_RB <- wide %>% filter(type == "RB") %>% select(-variable, -type) %>%
          rename(RB = value)
        wide_RP <- wide %>% filter(type == "RP") %>% select(-variable, -type) %>%
          rename(RP = value)
        wide_RT <- wide %>% filter(type == "RT") %>% select(-variable, -type) %>%
          rename(RT = value)

        l = list(wide_RB, wide_RT, wide_RP)
        df <- join_all(l, type = "full") %>% select(unique_ID, domain, Qnumber, RB, RP, RT)
        rm(wide)

        df <- df %>% arrange(unique_ID, domain, Qnumber)

        return(df)
      }

      df <- panelform(selectcol(df))
      # df <- mutate(df, id=as.numeric(factor(unique_ID)))
      return(df)
    }


    if (file_type == "csv") {
      df <- full.panel(uniqR_csv(df, var))
      return(df)

    } else if (file_type == "xml") {
      df <- full.panel(uniqR_xml(df, var))
      return(df)

    }
  }


  format.result <- function(df){
    result <- attr(df, "split_labels")
    for ( i in 1: dim(result)[1] ){
      result$int[i] <- df[[i]]$coefficients[1]
      result$RB[i] <- df[[i]]$coefficients[2]
      result$RP[i] <- df[[i]]$coefficients[3]
    }

    result <- merge(result, idlist, by="unique_ID") %>%
      select(unique_ID, domain, int, RB, RP)

    return(result)
  }

  if(file_type != "csv" & file_type != "xml"){
    print("file_type should be either .csv or .xml")
  } else{
    clean_df <- d_clean(df, var, file_type)
    reg <- dlply(clean_df, c("unique_ID", "domain"), function(data) lm(RT ~ RB + RP, data = data))
    domainlist <- distinct(select(clean_df, domain))
    idlist <- unique(select(clean_df, unique_ID))
    reg_result <- format.result(reg)
    split <- split(reg_result, reg_result$domain)
    list_df <- list()

    # see if fin.int -> fin_int

    for (i in 1:nrow(domainlist)){
      temp <- as.data.frame(split[i])[, -2]

      names(temp) <- ifelse(stringr::str_detect(names(temp), "unique_ID"),
                            "unique_ID", names(temp))
      assign(paste0("coef_", domainlist[i, ]), temp)

      colnames(temp)[2] <- paste0(domainlist[i, ], "_int")
      colnames(temp)[3] <- paste0(domainlist[i, ], "_RB")
      colnames(temp)[4] <- paste0(domainlist[i, ], "_RP")

      list_df[[i]] <- temp
    }

    full_coef <- Reduce(function(x,y) merge(x, y, all = TRUE, by = "unique_ID"), list_df)
    wide_temp <- wideformat(df, var, file_type)
    df <- merge(wide_temp, full_coef, by = "unique_ID")
    return(df)
  }
}


```

```{r, echo=T, warning=FALSE, message=FALSE}
#calculating means

F_M_RT <- dospert_norm_data %>%
    dplyr::select(finRT_1,finRT_2,finRT_3,finRT_4,finRT_5,finRT_6) %>%
    transmute(F_M_RT = rowMeans(.))

F_M_RB <- dospert_norm_data %>%
    dplyr::select(finRB_1,finRB_2,finRB_3,finRB_4,finRB_5,finRB_6) %>%
    transmute(F_M_RB = rowMeans(.))

F_M_RP <- dospert_norm_data %>%
    dplyr::select(finRP_1,finRP_2,finRP_3,finRP_4,finRP_5,finRP_6) %>%
    transmute(F_M_RP = rowMeans(.))


R_M_RT <- dospert_norm_data %>%
    dplyr::select(recRT_1,recRT_2,recRT_3,recRT_4,recRT_5,recRT_6) %>%
    transmute(R_M_RT = rowMeans(.))

R_M_RB <- dospert_norm_data %>%
    dplyr::select(recRB_1,recRB_2,recRB_3,recRB_4,recRB_5,recRB_6) %>%
    transmute(R_M_RB = rowMeans(.))

R_M_RP <- dospert_norm_data %>%
    dplyr::select(recRP_1,recRP_2,recRP_3,recRP_4,recRP_5,recRP_6) %>%
    transmute(R_M_RP = rowMeans(.))


S_M_RT <- dospert_norm_data %>%
    dplyr::select(socRT_1,socRT_2,socRT_3,socRT_4,socRT_5,socRT_6) %>%
    transmute(S_M_RT = rowMeans(.))

S_M_RB <- dospert_norm_data %>%
    dplyr::select(socRB_1,socRB_2,socRB_3,socRB_4,socRB_5,socRB_6) %>%
    transmute(S_M_RB = rowMeans(.))

S_M_RP <- dospert_norm_data %>%
    dplyr::select(socRP_1,socRP_2,socRP_3,socRP_4,socRP_5,socRP_6) %>%
    transmute(S_M_RP = rowMeans(.))

HS_M_RT <- dospert_norm_data %>%
    dplyr::select(heaRT_1,heaRT_2,heaRT_3,heaRT_4,heaRT_5,heaRT_6) %>%
    transmute(HS_M_RT = rowMeans(.))

HS_M_RB <- dospert_norm_data %>%
    dplyr::select(heaRB_1,heaRB_2,heaRB_3,heaRB_4,heaRB_5,heaRB_6) %>%
    transmute(HS_M_RB = rowMeans(.))

HS_M_RP <- dospert_norm_data %>%
    dplyr::select(heaRP_1,heaRP_2,heaRP_3,heaRP_4,heaRP_5,heaRP_6) %>%
    transmute(HS_M_RP = rowMeans(.))


E_M_RT <- dospert_norm_data %>%
    dplyr::select(ethRT_1,ethRT_2,ethRT_3,ethRT_4,ethRT_5,ethRT_6) %>%
    transmute(E_M_RT = rowMeans(.))

E_M_RB <- dospert_norm_data %>%
    dplyr::select(ethRB_1,ethRB_2,ethRB_3,ethRB_4,ethRB_5,ethRB_6) %>%
    transmute(E_M_RB = rowMeans(.))

E_M_RP <- dospert_norm_data %>%
    dplyr::select(ethRP_1,ethRP_2,ethRP_3,ethRP_4,ethRP_5,ethRP_6) %>%
    transmute(E_M_RP = rowMeans(.))

dospert_norm_data <- cbind(dospert_norm_data, F_M_RP, F_M_RB, F_M_RT, S_M_RP, S_M_RB, S_M_RT, E_M_RP, E_M_RB, E_M_RT, HS_M_RP, HS_M_RB, HS_M_RT, R_M_RP, R_M_RB, R_M_RT)

#dospert score 
dospert_score <- dd_score(dospert_norm_data, "serial", file_type = "csv")

saveRDS(dospert_score, "dospert_score1.rds")

dospert_score <- dospert_score %>% filter(rec_RP < 7)
```

#Descriptive Statistics: Demographics

###Gender
+   Female = 0
+   Male = 1
```{r, warning=FALSE, message=FALSE, fig.width=9}
plot_percent(dospert_norm_data,"Gender") + ggtitle('Gender') 
table(dospert_norm_data$Gender)
```
number of non-NA observations:**`r length(which(!(is.na(dospert_norm_data$Gender))))`**

###Birth year
```{r, echo=T, warning=FALSE, message=FALSE}
plot_hist(dospert_norm_data,"Age", bin1 = F) + ggtitle('Age')
summary(dospert_norm_data$Age) 
```
number of non-NA observations:**`r length(which(!(is.na(dospert_norm_data$Birth_Year))))`**

###Race
```{r, echo=T, warning=FALSE, message=FALSE}
plot_percent(dospert_norm_data,"Race") + ggtitle('Race')
table(dospert_norm_data$Race)
```

###Marital status
```{r, echo=T, warning=FALSE, message=FALSE}
plot_percent(dospert_norm_data,"Marital_Status") + ggtitle('Marital Status')
table(dospert_norm_data$Marital_Status)
```
number of non-NA observations:**`r length(which(!(is.na(dospert_norm_data$Marital_Status))))`**

###Children
```{r, echo=T, warning=FALSE, message=FALSE}
plot_percent(dospert_norm_data,"Children") + ggtitle('Children')
table(dospert_norm_data$Children)
```
number of non-NA observations:**`r length(which(!(is.na(dospert_norm_data$Children))))`**

###ethnicity
```{r, echo=T, warning=FALSE, message=FALSE}
plot_percent(dospert_norm_data,"Ethnicity") + ggtitle('Ethnicity')
table(dospert_norm_data$Ethnicity)
```
number of non-NA observations:**`r length(which(!(is.na(dospert_norm_data$Ethnicity))))`**

###education
```{r, echo=T, warning=FALSE, message=FALSE}
plot_percent(dospert_norm_data,"Education") + ggtitle('Education')
table(dospert_norm_data$Education)
```
number of non-NA observations:**`r length(which(!(is.na(dospert_norm_data$Education))))`**

###Political
+   1 = Democrat
+   2 = Independent
+   3 = Republican
```{r, echo=T, warning=FALSE, message=FALSE}
plot_percent(dospert_norm_data,"Political1") + ggtitle('Political')
table(dospert_norm_data$Political1)
```
number of non-NA observations:**`r length(which(!(is.na(dospert_norm_data$Political))))`**

###Income
```{r, echo=T, warning=FALSE, message=FALSE}
plot_percent(dospert_norm_data,"Income") + ggtitle('Income')
table(dospert_norm_data$Income)
```
number of non-NA observations:**`r length(which(!(is.na(dospert_norm_data$Children))))`**


#Descriptive Statistics: DOSPERT Means
mean scores for risk-taking, risk-perception, and risk-benefit for financial, social, recreational, ethical, and health/safety separately

###Financial

+   Dashed line = median, solid line = mean   

```{r, echo=T, warning=FALSE, message=FALSE}
ggplot(dospert_norm_data, aes(x=F_M_RT)) + 
  geom_histogram(fill="grey", color="blue", binwidth = .5) +
  geom_vline(aes(xintercept=mean(F_M_RT, na.rm=T)),
             color="yellow", 
             #linetype="dashed", 
             size=1) +
  geom_vline(aes(xintercept=median(F_M_RT, na.rm=T)),
             color="yellow", 
             linetype="dashed",
             size=1)
```

+   Red = Risk Perception
+   Blue = Risk Benefit

```{r, echo=FALSE, message=FALSE}
#Random numbers
h1 <- dospert_norm_data$F_M_RP
h2 <- dospert_norm_data$F_M_RB

# Histogram Colored (blue and red)
hist(h1, col=rgb(1,0,0,0.5), xlim=c(1,7), ylim=c(0,400), 
     main="Financial",
     xlab="")
hist(h2, col=rgb(0,0,1,0.5), add=T)
box()

```


###Social
+   Dashed line = median, solid line = mean   
```{r, echo=T, warning=FALSE, message=FALSE}
ggplot(dospert_norm_data, aes(x=S_M_RT)) + 
  geom_histogram(fill="grey", color="blue", binwidth = .5) +
  geom_vline(aes(xintercept=mean(S_M_RT, na.rm=T)),
             color="yellow", 
             #linetype="dashed", 
             size=1) +
  geom_vline(aes(xintercept=median(S_M_RT, na.rm=T)),
             color="yellow", 
             linetype="dashed",
             size=1)
```

+   Red = Risk Perception
+   Blue = Risk Benefit
```{r, echo=FALSE, message=FALSE}
#Random numbers
h1 <- dospert_norm_data$S_M_RP
h2 <- dospert_norm_data$S_M_RB

# Histogram Colored (blue and red)
hist(h1, col=rgb(1,0,0,0.5), xlim=c(1,7), ylim=c(1,400), 
     main="Social",
     xlab="")
hist(h2, col=rgb(0,0,1,0.5), add=T)
box()

```

###Health/Safety

+   Dashed line = median, solid line = mean   
```{r, echo=T, warning=FALSE, message=FALSE}
ggplot(dospert_norm_data, aes(x=HS_M_RT)) + 
  geom_histogram(fill="grey", color="blue", binwidth = .5) +
  geom_vline(aes(xintercept=mean(HS_M_RT, na.rm=T)),
             color="yellow", 
             #linetype="dashed", 
             size=1) +
  geom_vline(aes(xintercept=median(HS_M_RT, na.rm=T)),
             color="yellow", 
             linetype="dashed",
             size=1)
```

+   Red = Risk Perception
+   Blue = Risk Benefit
```{r, echo=FALSE, message=FALSE}
#Random numbers
h1 <- dospert_norm_data$HS_M_RP
h2 <- dospert_norm_data$HS_M_RB

# Histogram Colored (blue and red)
hist(h1, col=rgb(1,0,0,0.5), xlim=c(1,7), ylim=c(0,1000), 
     main="Health/Safety",
     xlab="")
hist(h2, col=rgb(0,0,1,0.5), add=T)
box()

```


###Recreational
+   Dashed line = median, solid line = mean   
```{r, echo=T, warning=FALSE, message=FALSE}
ggplot(dospert_norm_data, aes(x=R_M_RT)) + 
  geom_histogram(fill="grey", color="blue", binwidth = .5) +
  geom_vline(aes(xintercept=mean(R_M_RT, na.rm=T)),
             color="yellow", 
             #linetype="dashed", 
             size=1) +
  geom_vline(aes(xintercept=median(R_M_RT, na.rm=T)),
             color="yellow", 
             linetype="dashed",
             size=1)
```

+   Red = Risk Perception
+   Blue = Risk Benefit
```{r, echo=FALSE, message=FALSE}
#Random numbers
h1 <- dospert_norm_data$R_M_RP
h2 <- dospert_norm_data$R_M_RB

# Histogram Colored (blue and red)
hist(h1, col=rgb(1,0,0,0.5), xlim=c(1,7), ylim=c(0,400), 
     main="Recreational",
     xlab="")
hist(h2, col=rgb(0,0,1,0.5), add=T)
box()

```


###Ethical (eth)
+   Dashed line = median, solid line = mean   
```{r, echo=T, warning=FALSE, message=FALSE}
ggplot(dospert_norm_data, aes(x=E_M_RT)) + 
  geom_histogram(fill="grey", color="blue", binwidth = .5) +
  geom_vline(aes(xintercept=mean(E_M_RT, na.rm=T)),
             color="yellow", 
             #linetype="dashed", 
             size=1) +
  geom_vline(aes(xintercept=median(E_M_RT, na.rm=T)),
             color="yellow", 
             linetype="dashed",
             size=1)
```

+   Red = Risk Perception
+   Blue = Risk Benefit
```{r, echo=FALSE, message=FALSE}
#Random numbers
h1 <- dospert_norm_data$E_M_RP
h2 <- dospert_norm_data$E_M_RB

# Histogram Colored (blue and red)
hist(h1, col=rgb(1,0,0,0.5), xlim=c(1,7), ylim=c(0,400), 
     main="Ethial",
     xlab="")
hist(h2, col=rgb(0,0,1,0.5), add=T)
box()

```



```{r, echo=T, warning=FALSE, message=FALSE}
#dospert sum
#dospert_sum <- d_sum(dospert_norm_data, "serial", "fin", "RT", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "fin", "RP", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "fin", "RB", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "eth", "RT", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "eth", "RP", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "eth", "RB", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "soc", "RT", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "soc", "RP", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "soc", "RB", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "rec", "RT", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "rec", "RP", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "rec", "RB", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "hea", "RT", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "hea", "RP", file_type = "csv")
#dospert_sum <- d_sum(dospert_norm_data, "serial", "hea", "RB", file_type = "csv")

```


#DOSPERT Score
+   Positive coef(b) = risk seeking behavior, Negative coef(b) = risk aversion behavior
+   Preference (X) = a(Expected Benefit(X)) + b(Perceived Risk(X)) + c 

###Financial
+   Positive coef(b) = risk seeking behavior, Negative coef(b) = risk aversion behavior
+   Preference (X) = a(Expected Benefit(X)) + b(Perceived Risk(X)) + c 
+   Red = a (Percieved Risk)
+   Blue = b (Risk Benefit)
```{r, echo=FALSE, message=FALSE}

ggplot(dospert_score, aes(x=fin_RP)) + 
  geom_histogram(fill="grey", color="blue", binwidth = .5) +
  geom_vline(aes(xintercept=mean(fin_RP, na.rm=T)),
             color="yellow", 
             #linetype="dashed", 
             size=1) +
  geom_vline(aes(xintercept=median(fin_RP, na.rm=T)),
             color="yellow", 
             linetype="dashed",
             size=1)
```

###Social
+   Positive coef(b) = risk seeking behavior, Negative coef(b) = risk aversion behavior
+   Preference (X) = a(Expected Benefit(X)) + b(Perceived Risk(X)) + c 
+   Red = a (Percieved Risk)
+   Blue = b (Risk Benefit)
```{r, echo=FALSE, message=FALSE}
#Random numbers

ggplot(dospert_score, aes(x=soc_RP)) + 
  geom_histogram(fill="grey", color="blue", binwidth = .5) +
  geom_vline(aes(xintercept=mean(soc_RP, na.rm=T)),
             color="yellow", 
             #linetype="dashed", 
             size=1) +
  geom_vline(aes(xintercept=median(soc_RP, na.rm=T)),
             color="yellow", 
             linetype="dashed",
             size=1)
```


###Health/Safety
+   Positive coef(b) = risk seeking behavior, Negative coef(b) = risk aversion behavior
+   Preference (X) = a(Expected Benefit(X)) + b(Perceived Risk(X)) + c 
+   Red = a (Percieved Risk)
+   Blue = b (Risk Benefit)
```{r, echo=FALSE, message=FALSE}
#Random numbers
ggplot(dospert_score, aes(x=hea_RP)) + 
  geom_histogram(fill="grey", color="blue", binwidth = .5) +
  geom_vline(aes(xintercept=mean(hea_RP, na.rm=T)),
             color="yellow", 
             #linetype="dashed", 
             size=1) +
  geom_vline(aes(xintercept=median(hea_RP, na.rm=T)),
             color="yellow", 
             linetype="dashed",
             size=1)
```


###Recreational
+   Positive coef(b) = risk seeking behavior, Negative coef(b) = risk aversion behavior
+   Preference (X) = a(Expected Benefit(X)) + b(Perceived Risk(X)) + c 
+   Red = a (Percieved Risk)
+   Blue = b (Risk Benefit)
```{r, echo=FALSE, message=FALSE}
#Random numbers
ggplot(dospert_score, aes(x=rec_RP)) + 
  geom_histogram(fill="grey", color="blue", binwidth = .5) +
  geom_vline(aes(xintercept=mean(rec_RP, na.rm=T)),
             color="yellow", 
             #linetype="dashed", 
             size=1) +
  geom_vline(aes(xintercept=median(rec_RP, na.rm=T)),
             color="yellow", 
             linetype="dashed",
             size=1)

```


###Ethical
+   Positive coef(b) = risk seeking behavior, Negative coef(b) = risk aversion behavior
+   Preference (X) = a(Expected Benefit(X)) + b(Perceived Risk(X)) + c 
+   Red = a (Percieved Risk)
+   Blue = b (Risk Benefit)
```{r, echo=FALSE, message=FALSE}
#Random numbers
ggplot(dospert_score, aes(x=eth_RP)) + 
  geom_histogram(fill="grey", color="blue", binwidth = .5) +
  geom_vline(aes(xintercept=mean(eth_RP, na.rm=T)),
             color="yellow", 
             #linetype="dashed", 
             size=1) +
  geom_vline(aes(xintercept=median(eth_RP, na.rm=T)),
             color="yellow", 
             linetype="dashed",
             size=1)
```

#Regressions: Financial

###Age
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
summary(model1 <- lm(F_M_RT ~ Age, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Age Predicting Mean Financial Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Gender
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
summary(model1 <- lm(F_M_RT ~ Gender, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Gender Predicting Mean Financial Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Political Affiliation
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

#making political a continuous variable 
dospert_norm_data$Political1 <- as.numeric(dospert_norm_data$Political1) 
summary(model1 <- lm(F_M_RT ~ Political1, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Political Affiliation Predicting Mean Financial Risk-Taking',
        caption.above = TRUE, digits = 4)

```



###Education Level
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

dospert_norm_data$Education <- as.numeric(dospert_norm_data$Education) 
summary(model1 <- lm(F_M_RT ~ Education, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Education Level Predicting Mean Financial Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Income Level
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

dospert_norm_data$Income <- as.numeric(dospert_norm_data$Income)
summary(model1 <- lm(F_M_RT ~ Income, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Income Predicting Financial Risk-Taking',
        caption.above = TRUE, digits = 4)

```


###Total Item
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

summary(model1 <- lm(F_M_RT ~ Age + Gender + Political1 + Education + Income, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'All Items Predicting Mean Financial Risk-Taking',
        caption.above = TRUE, digits = 4)

```



#Regressions: Social

###Age
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
summary(model1 <- lm(S_M_RT ~ Age, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Age Predicting Mean Social Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Gender
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
summary(model1 <- lm(S_M_RT ~ Gender, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Gender Predicting Mean Social Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Political Affiliation
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

summary(model1 <- lm(S_M_RT ~ Political1, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Political Affiliation Predicting Social Risk-Taking',
        caption.above = TRUE, digits = 4)

```



###Education Level
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

dospert_norm_data$Education <- as.numeric(dospert_norm_data$Education) 
summary(model1 <- lm(S_M_RT ~ Education, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Education Level Predicting Social Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Income Level
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

summary(model1 <- lm(S_M_RT ~ Income, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Income Predicting Ethical Risk-Taking',
        caption.above = TRUE, digits = 4)

```


###Total Item
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

summary(model1 <- lm(S_M_RT ~ Age + Gender + Political1 + Education + Income, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'All Items Predicting Mean Social Risk-Taking',
        caption.above = TRUE, digits = 4)

```



#Regressions: Health/Safety

###Age
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
summary(model1 <- lm(HS_M_RT ~ Age, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Age Predicting Mean Health/Safety Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Gender
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
summary(model1 <- lm(HS_M_RT ~ Gender, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Gender Predicting Mean Health/Safety Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Political Affiliation
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

dospert_norm_data$Political1 <- as.numeric(dospert_norm_data$Political1) 
summary(model1 <- lm(HS_M_RT ~ Political1, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Political Affiliation Predicting Health/Safety Risk-Taking',
        caption.above = TRUE, digits = 4)

```



###Education Level
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

dospert_norm_data$Education <- as.numeric(dospert_norm_data$Education) 
summary(model1 <- lm(HS_M_RT ~ Education, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Education Level Predicting Health/Safety Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Income Level
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

summary(model1 <- lm(HS_M_RT ~ Income, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Income Predicting Health/Safety Risk-Taking',
        caption.above = TRUE, digits = 4)

```


###Total Item
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

summary(model1 <- lm(HS_M_RT ~ Age + Gender + Political1 + Education + Income, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'All Items Predicting Mean Health/Safety Risk-Taking',
        caption.above = TRUE, digits = 4)

```



#Regressions: Recreational

###Age
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
summary(model1 <- lm(R_M_RT ~ Age, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Age Predicting Mean Recreational Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Gender
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
summary(model1 <- lm(R_M_RT ~ Gender, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Gender Predicting Mean Recreational Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Political Affiliation
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

dospert_norm_data$Political1 <- as.numeric(dospert_norm_data$Political1) 
summary(model1 <- lm(R_M_RT ~ Political1, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Political Affiliation Recreational Financial Risk-Taking',
        caption.above = TRUE, digits = 4)

```



###Education Level
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

dospert_norm_data$Education <- as.numeric(dospert_norm_data$Education) 
summary(model1 <- lm(R_M_RT ~ Education, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Education Level Predicting Recreational Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Income Level
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

summary(model1 <- lm(R_M_RT ~ Income, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Income Predicting Ethical Risk-Taking',
        caption.above = TRUE, digits = 4)

```


###Total Item
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

summary(model1 <- lm(R_M_RT ~ Age + Gender + Political1 + Education + Income, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'All Items Predicting Mean Recreational Risk-Taking',
        caption.above = TRUE, digits = 4)

```



#Regressions: Ethical

###Age
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
summary(model1 <- lm(E_M_RT ~ Age, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Age Predicting Mean Ethical Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Gender
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}
summary(model1 <- lm(E_M_RT ~ Gender, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Gender Predicting Mean Ethical Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Political Affiliation
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

dospert_norm_data$Political1 <- as.numeric(dospert_norm_data$Political1) 
summary(model1 <- lm(E_M_RT ~ Political1, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Political Affiliation Predicting Ethical Risk-Taking',
        caption.above = TRUE, digits = 4)

```



###Education Level
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

dospert_norm_data$Education <- as.numeric(dospert_norm_data$Education) 
summary(model1 <- lm(E_M_RT ~ Education, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Education Level Predicting Ethical Risk-Taking',
        caption.above = TRUE, digits = 4)

```

###Income Level
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

summary(model1 <- lm(E_M_RT ~ Income, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'Income Predicting Ethical Risk-Taking',
        caption.above = TRUE, digits = 4)

```


###Total Item
```{r, echo=F, warning=FALSE, message=FALSE, echo=FALSE, results='asis'}

summary(model1 <- lm(E_M_RT ~ Age + Gender + Political1 + Education + Income, data = dospert_norm_data))



htmlreg(l = list(model1),
        center = TRUE, stars = c(0.001, 0.01, 0.05, 0.1),
        bold = 0.1, caption = 'All Items Predicting Mean Ethical Risk-Taking',
        caption.above = TRUE, digits = 4)

```

#Sploms 

###Risk-taking
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=14, fig.height=14}
#eval = F in the r chunk if you don't want it to be evaluated (comment it out)

#changing class to integer
dospert_norm_data$F_M_RT <- as.integer(dospert_norm_data$F_M_RT)
dospert_norm_data$E_M_RT <- as.integer(dospert_norm_data$E_M_RT)
dospert_norm_data$S_M_RT <- as.integer(dospert_norm_data$S_M_RT)
dospert_norm_data$HS_M_RT <- as.integer(dospert_norm_data$HS_M_RT)
dospert_norm_data$R_M_RT <- as.integer(dospert_norm_data$R_M_RT)


decider::splom_CDS(dospert_norm_data %>% select(F_M_RT, E_M_RT, S_M_RT, R_M_RT, HS_M_RT), 
                   plotTitle = "Predicting risk-taking by domain (using means)")

```

###Risk-benefit
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=14, fig.height=14}
#eval = F in the r chunk if you don't want it to be evaluated (comment it out)

#changing class to integer
dospert_norm_data$F_M_RB <- as.integer(dospert_norm_data$F_M_RB)
dospert_norm_data$E_M_RB <- as.integer(dospert_norm_data$E_M_RB)
dospert_norm_data$S_M_RB <- as.integer(dospert_norm_data$S_M_RB)
dospert_norm_data$HS_M_RB <- as.integer(dospert_norm_data$HS_M_RB)
dospert_norm_data$R_M_RB <- as.integer(dospert_norm_data$R_M_RB)

decider::splom_CDS(dospert_norm_data %>% select(F_M_RB, E_M_RB, S_M_RB, R_M_RB, HS_M_RB), 
                   plotTitle = "Predicting risk-benefit by domain (using means)")

```


###Risk-perception
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=14, fig.height=14}
#eval = F in the r chunk if you don't want it to be evaluated (comment it out)

#making changing class to integer
dospert_norm_data$F_M_RP <- as.integer(dospert_norm_data$F_M_RP)
dospert_norm_data$E_M_RP <- as.integer(dospert_norm_data$E_M_RP)
dospert_norm_data$S_M_RP <- as.integer(dospert_norm_data$S_M_RP)
dospert_norm_data$HS_M_RP <- as.integer(dospert_norm_data$HS_M_RP)
dospert_norm_data$R_M_RP <- as.integer(dospert_norm_data$R_M_RP)


decider::splom_CDS(dospert_norm_data %>% select(F_M_RP, E_M_RP, S_M_RP, R_M_RP, HS_M_RP), 
                   plotTitle = "Predicting risk-perception by domain (using means)")

```
